Spec2Fab: A Graph-Based Framework for Fabricating Fabrication Algorithms

### 2012-12-21 paper.tex
add result table

\note{I think we should just go with the results we have, texture etc... show the reducer network, tuner network, simulated results and manufactured result (if you have them}
\section{Results and Discussion}
Table~\ref{tab:built-in} shows a list of nodes implemented in our framework. With this set of nodes we can reproduce all work previously discussed. This validates our assertion, that the space of fabrication  algorithms can be spanned effectively using the Reducer and Tuner networks. Secondly it illustrates how we can leverage component reuse to quickly create such algorithms.\autoref{tab:example} lists the components of the framework used to recreate each example.
\begin{table*}
\centering
\begin{tabular}{lc}
\hline 
\textbf{Reducer Node} & \textbf{Description} \\
Geometry Nodes &\\
\hline
InputMesh & Loads shape to which materials will be assigned\\\
Stratum & Divides an input volume into an outer layer of given thickness and an interior blob\\
Column & Divides an input volume into a number of columns\\
\hline
Material Nodes &\\
\hline
ConstantMaterial & Assigns a constant material to an input volume \\
LayeredMaterial &  Assigns a layered set of materials to an input volume \\
QuadLayerMaterial & Like LayeredMaterial, but the materials are separated by a quadrangle\\
SubdivSurfMateral & Like LayeredMaterial, but the materials are separated by a subdivision surface \\
\hline
\end{tabular}
\caption{Components we implemented and used in the experiments.}
\label{tab:built-in}
\end{table*}

\begin{table*}
\centering
\begin{tabular}{llll}  %error metric is not interesting
\hline 
\textbf{Example} & \textbf{Reducer Nodes} & \textbf{Simulator} & \textbf{Optimization}\\
\hline 
Texture& Stratum, Column, LayeredMaterial & reflectance & Error diffusion \\
Subsurface scattering& Stratum, Column, LayeredMaterial & reflectance , transmittance & Branch and bound\\
Caustics 1 & Column, QuadLayerMaterial & & SA \\
Caustics 2 & Column, SubdivSurfMaterial & caustics & SPSA \\
Deformation & Column, LayeredMaterial& elasticity & Branch and bound\\
\hline
\end{tabular}
\caption{Components we implemented and used in the experiments.}
\label{tab:example}
\end{table*}

>>>>

\note{I think we should just go with the results we have, texture etc... show the reducer network, tuner network, simulated results and manufactured result (if you have them}
\section{Results and Discussion}
Table~\ref{tab:built-in} shows a list of nodes implemented in our framework. With this set of nodes we can reproduce all work previously discussed. This validates our assertion, that the space of fabrication  algorithms can be spanned effectively using the Reducer and Tuner networks. Secondly it illustrates how we can leverage component reuse to quickly create such algorithms.\autoref{tab:example} lists the components of the framework used to recreate each example.

For each example, we show the target, the simulated output, and the fabricated result in Figure~\ref{tab:result}.

\begin{table*}
\centering
\begin{tabular}{lc}
\hline 
\textbf{Reducer Node} & \textbf{Description} \\
Geometry Nodes &\\
\hline
InputMesh & Loads shape to which materials will be assigned\\\
Stratum & Divides an input volume into an outer layer of given thickness and an interior blob\\
Column & Divides an input volume into a number of columns\\
\hline
Material Nodes &\\
\hline
ConstantMaterial & Assigns a constant material to an input volume \\
LayeredMaterial &  Assigns a layered set of materials to an input volume \\
QuadLayerMaterial & Like LayeredMaterial, but the materials are separated by a quadrangle\\
SubdivSurfMateral & Like LayeredMaterial, but the materials are separated by a subdivision surface \\
\hline
\end{tabular}
\caption{Components we implemented and used in the experiments.}
\label{tab:built-in}
\end{table*}

\begin{table*}
\centering
\begin{tabular}{|l|l|l|l|}
\hline 
\textbf{Example} & \textbf{Target} & \textbf{Simulation} & \textbf{Printed Result}\\
\hline 
Texture&  \includegraphics[width=3cm]{figure/globeTarget.png}& \includegraphics[width=3cm]{figure/globeSim.png}
& \includegraphics[width=3cm]{figure/globe.png}\\
&  \includegraphics[width=3cm]{figure/mapTarget.png}& \includegraphics[width=3cm]{figure/mapSim.png}
& \includegraphics[width=3cm]{figure/map.png}\\
\hline
\end{tabular}
\caption{Components we implemented and used in the experiments.}
\label{tab:example}
\end{table*}

\begin{table*}
\centering
\begin{tabular}{llll}  %error metric is not interesting
\hline 
\textbf{Example} & \textbf{Reducer Nodes} & \textbf{Simulator} & \textbf{Optimization}\\
\hline 
Texture& Stratum, Column, LayeredMaterial & reflectance & Error diffusion \\
Subsurface scattering& Stratum, Column, LayeredMaterial & reflectance , transmittance & Branch and bound\\
Caustics 1 & Column, QuadLayerMaterial & & SA \\
Caustics 2 & Column, SubdivSurfMaterial & caustics & SPSA \\
Deformation & Column, LayeredMaterial& elasticity & Branch and bound\\
\hline
\end{tabular}
\caption{Fabricated results.}
\label{tab:result}
\end{table*}
